\chapter{Background}
The system is split into three different parts, the website, raspberry pi and the cloud(Azure).



\section{Website}
A website often confused with a webpage or a web server. From mozillaWebDoc, A website is a collection of web pages which are grouped together in various ways. A web server hosts websites and their supporting files are available on the that computer. 
How do they talk to each other?
A website talks to the webserver using an API, which is a connection between to computer programs. It could be referred also as the specification or as the implementation, the specification has to do with a document that demonstrates how to use or create a connection. Examples of API specifications used in this project are; tedious for the database connection to azure, express as a middleware. 

MVC architecture.

middleware for NodeJS.
\newacronym{API}{$API$}{Application Programming Interface}
\glsadd{API}
reason for a website is to allow the Admin or Lecturer access this system from anywhere so that he can start tracking attendance from anywhere.

\section{Raspberry pi}
A portable computer with 40 GPIO pins, 
GPIO is an uncommitted digital pin on an electronic circuit board which may be used as input or output or both, and can be configured by the user at runtime[6]. This GPIO allows to interface with different modules. A module here is a small unit that can be integrated into a larger system but also maintained separately with no effect on the system. It is of a "plug-in" functionality.

\newacronym{GPIO}{$GPIO$}{General Purpose Input Output}
\glsadd{GPIO}

\subsection{RFID}
The RFID card interfaces with the raspberry-pi with SPI, it is a synchronous serial communication that encourages communication over a short distance, it is mainly used in embedded systems. Serial communication has to do with sending one bit at a time sequentially and synchronous means that this communication is synchronized by a clock signal which is used orchestrate the actions of the digital circuit i.e to determine when it is time to read the next bit/value. SPI devices communicate in a full duplex mode with a master-slave principle normally with a single master


\newacronym{SPI}{$SPI$}{Serial Peripheral Interface}
\glsadd{SPI}





LED 



\subsection{Fingerprint}



\section{Cloud}




